IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-07-27 review/response_2.tex

\documentclass{article}

\usepackage[T1]{fontenc}
\usepackage[short]{optidef}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{adjustbox}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{cite}
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{microtype}
\usepackage{multirow}
\usepackage{pdfpages}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{xr-hyper}
\usepackage{hyperref}

\externaldocument[M-]{submit}

\DeclareSIUnit{\belm}{Bm}
\DeclareSIUnit{\dBm}{\deci\belm}
\DeclareSIUnit{\beli}{Bi}
\DeclareSIUnit{\dBi}{\deci\beli}

\newcounter{reviewer}
\setcounter{reviewer}{0}
\newcounter{point}[reviewer]
\setcounter{point}{0}
\newcounter{response}[reviewer]
\setcounter{response}{0}

\let\svbibcite\bibcite
\def\bibcite#1#2{\svbibcite{#1}{R#2}}
\makeatletter
\let\svbiblabel\@biblabel
\def\@biblabel#1{\svbiblabel{R#1}}
\makeatother

\renewcommand{\theequation}
	{E\arabic{equation}}

\renewcommand{\thefigure}
	{F\arabic{figure}}

\renewcommand{\thetable}
	{T\arabic{table}}

\renewcommand{\thealgorithm}
	{A\arabic{algorithm}}

\newcommand{\reviewer}
	{\stepcounter{reviewer} \bigskip \hrule \section*{Reviewer \thereviewer}}

\renewcommand{\thepoint}
	{\thereviewer.\arabic{point}}

\renewcommand{\theresponse}
	{\thereviewer.\arabic{response}}

\newenvironment{point}
	{\refstepcounter{point} \bigskip \noindent {\textbf{Comment~\thepoint} } ---\ \itshape}
	{\par}

\newenvironment{response}
	{\refstepcounter{response} \medskip \noindent \textbf{Response:}\ }
	{\medskip}

\begin{document}
	\includepdf{letter_1.pdf}

	\begin{reviewer}
		\begin{point}
			As this paper proposed a BCD-based algorithm and LC-BCD algorithm, it could be better if the authors can further discuss the complexity and provide some measurements or some simulation results.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			Since this paper focused on IRS-aided SWIPT systems, it could be better if the authors can further enrich the survey part to make the paper more comprehensive. In particular, some papers have considered this kind of problem from a different aspect such as \cite{Xu2021}. It is kindly suggested to briefly discuss the main difference between \cite{Xu2021} and the problem considered in this paper.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			It could be better if the authors can provide some references for the parameter values chosen in the simulation part.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			The reviewer noticed that in Algorithm 5, there are two convergence criteria. It could be better if the authors can briefly interpret this issue.
		\end{point}

		\begin{response}
			TODO
		\end{response}
	\end{reviewer}

	\begin{reviewer}
		\begin{point}
			Although this paper reveals many useful insights, most of them are obtained via simulation and then explained via text. The overall theoretical contributions can be greatly improved if the authors can analytically verify or prove some of them, especially those unique to this paper. The authors may conduct the analysis under some simplified or special cases. If some of the observations and findings have been verified in existing papers, the authors can cite and echo these papers wherever necessary.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			The authors are suggested to study the impact of IRS passive beamforming on the waveform design without IRS. For example, they can show the optimized waveforms with versus without IRS to unveil the interplay between them. Or even better, analytically compare the two waveforms.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			In the introduction, it is suggested to also discuss the new design challenges posed by the nonlinear model compared to the existing designs under the linear model.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			In (14), the authors integrated the waveform design and active beamforming design into $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$. However, they separately optimized them later. Is it possible to directly optimize $\boldsymbol{w}_I$ and $\boldsymbol{w}_P$ as a whole?
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			In the low-complexity BCD, it is unclear how the authors dealt with the optimization of $\rho$ and $\delta$. In Algorithm 5, both of them are input. Did the authors perform a two-dimensional search here? Besides, they were assumed to be identical in the simulation. How will this assumption influence the performance loss?
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			If possible, in Fig.11, the authors can show the performance of the design under the conventional linear harvester model, so as to show how much performance loss it would incur.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			It was shown via simulation that PS is not always superior to TS, unlike the linear model. Is it possible to develop some analytical preconditions to determine which one is better?
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			Is it possible to give the complexity order of the algorithms presented in this paper?
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			The expressions of signals in (1), (2), and (5) are not conventional. It may be better to give a per-band signal instead of their superposition. Besides, it is better to first introduce the functionalities of the modulated and multisine waveforms before giving (1).
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			In Remark 2, the meaning of the sentence, ``there exists a tradeoff for auxiliary link control in the frequency domain'', is not clear to me.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			Some editorial comments: 1) ``a (-->an) M-antenna''; 2) ``through a (-->an) L-element IRS''; 3) ``the CSIT of direct and cascaded channels are (-->is) known''; 4) ``It demonstrated (-->demonstrates) that''; 5) In Figs. 9(b) and 10(b), the text in the y-axis is too long. Please divide it into two rows. Besides, the text in the x-axis of the upper figure is covered by the lower one.
		\end{point}

		\begin{response}
			TODO
		\end{response}
	\end{reviewer}

	\begin{reviewer}
		\begin{point}
			Proposition 5 is questionable. The algorithm may not converge to a local optimal due to the coupling constraint 14b.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			The figures are too small. For example, Fig 10, the axis legend is not fully shown.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			It is said that the reference path loss is -35 dB at 1m, while for the center frequency at 5.18 GHz, even adopting the free space path loss model also will lead a much sever path loss at 1 m. It is not clear how the authors calculate this.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			The authors considered the practical reflection coefficient beamforming in the simulkation results. It is not cleaer how the authors obtain the discrte phase shift results. Direct quantization method and some other customized optimization technqiues for discrete phase shifts may have significant performance gap, see \cite{Wu2020c}. Also, this work adopts the same uniform quantization as the above work, which thus needs to be clarified in the paper.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			There are also some other practical phase shift models and nonlinear energy harvesting models such as saturation model for IRS-aided SWIPT in existing works, which may be discussed as related works such as amplitude-dependent phase shift model.
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			Some early magazine papers and recent tutorial papers related to IRS-aided WPT/WIT may be further discussed.
		\end{point}

		\begin{response}
			TODO
		\end{response}
	\end{reviewer}

	\begin{reviewer}
		\begin{point}
			What is the computational complexity of the proposed algorithm?
		\end{point}

		\begin{response}
			TODO
		\end{response}

		\begin{point}
			Some related works are worth citing, such as \cite{Yang2021}.
		\end{point}

		\begin{response}
			TODO
		\end{response}
	\end{reviewer}

	\bibliographystyle{IEEEtran}
	\bibliography{IEEEabrv,library.bib}
\end{document}

### 2021-07-28 main.tex
:pencil: Update manuscript

		\begin{subsection}{Low-Complexity Adaptive Design}
			To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF in the time and power domains. For WIT, the optimal WF strategy assigns the amplitude of modulated tone $n$ by
			\begin{equation}\label{eq:wf}
				s_{\mathrm{I}, n} = \sqrt{2\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+},
			\end{equation}
			where $\lambda$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$. The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here. On the other hand, SMF was proposed in \cite{Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
			\begin{equation}\label{eq:smf}
				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha,
			\end{equation}
			where the scaling ratio $\alpha \ge 1$ is given and can be adjusted to exploit the rectifier nonlinearity and frequency selectivity. When the receiver works in TS mode, there is no superposition in the suboptimal waveform design. Modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session. When the receiver works in PS mode, we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
			\begin{align}
				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha. \label{eq:s_p}
			\end{align}
			Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes. To achieve the WIT point (i.e., $\eta=\rho=0$), the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized. To achieve any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$. The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode. The proofs of SDR tightness and local optimality are similar to Appendices~\ref{ap:relaxation} and \ref{ap:sca} thus omitted here. Compared with Algorithm~\ref{al:sca}, the rate constraint \eqref{co:irs_rate} is dropped and each SDP in Algorithm~\ref{al:m_sca} involves $(L+1)$ linear constraints. Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010}.

@@

			For the low-complexity design, when the receiver works in PS mode, we instead obtain the phase shift by Algorithm~\ref{al:m_sca} and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}. The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}. Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{Luo2010}.

			\begin{algorithm}[!t]
				\caption{LC-BCD: Waveform and Beamforming.}
				\label{al:lc_bcd}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\delta$, $\rho$, $\epsilon$, $\forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
					\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:m_sca}
						\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)}$, $\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
						\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
					\Until $\lvert R^{(i)} - R^{(i-1)} \rvert \le \epsilon$ or $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$
				\end{algorithmic}
			\end{algorithm}
		\end{subsection}
	\end{section}

>>>>

		\begin{subsection}{Low-Complexity Adaptive Design}
			To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF in the time and power domains. For WIT, the optimal WF strategy assigns the amplitude of modulated tone $n$ by
			\begin{equation}\label{eq:wf}
				s_{\mathrm{I}, n} = \sqrt{2\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+},
			\end{equation}
			where $\lambda$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$. The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here. On the other hand, SMF was proposed in \cite{Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
			\begin{equation}\label{eq:smf}
				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha,
			\end{equation}
			where the scaling ratio $\alpha \ge 1$ is given and can be adjusted to exploit the rectifier nonlinearity and frequency selectivity. When the receiver works in TS mode, there is no superposition in the suboptimal waveform design. Modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session. When the receiver works in PS mode, we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
			\begin{align}
				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha. \label{eq:s_p}
			\end{align}
			Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes. To achieve the WIT point (i.e., $\eta=\rho=0$), the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized. In such case, the current expression is dropped and no SCA is involved. To achieve any non-WIT point (i.e., $z \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$. The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode. The proofs of SDR tightness and local optimality are similar to Appendices~\ref{ap:relaxation} and \ref{ap:sca} thus omitted here. Compared with Algorithm~\ref{al:sca}, the rate constraint \eqref{co:irs_rate} is dropped and each SDP in Algorithm~\ref{al:m_sca} involves $(L+1)$ linear constraints. Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010}. Note that $I_{\mathrm{M-SCA}}=1$ for the WIT point since the current expression is dropped and no SCA is involved.

@@

			For the low-complexity design, when the receiver works in PS mode, we instead obtain the phase shift by Algorithm~\ref{al:m_sca} and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}. In contrast to the BCD algorithm that obtains the R-E region by varying the rate constraint from maximum capacity $C_{\max}$\footnote{Recall in Remark~\ref{re:subband_tradeoff} that passive beamforming enables a resource allocation opportunity at the channel such that different capacities are achievable.} to \num{0}, the LC-BCD algorithm draws the R-E tradeoff by adjusting the combining and splitting ratios from \num{1} to \num{0}. For the WIT point, $C_{\max}$ can be obtained as a special case of LC-BCD algorithm where $\rho=0$ and the objective function becomes $R$ instead of $z$. The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}. Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{Luo2010}.

			\begin{algorithm}[!t]
				\caption{LC-BCD: Waveform and Beamforming.}
				\label{al:lc_bcd}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2$, $\beta_4$, $\boldsymbol{h}_{\mathrm{D},n}$, $\boldsymbol{V}_{n}$, $P$, $\sigma_n$, $\delta$, $\rho$, $\epsilon$, $\forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)}$, $\boldsymbol{b}_{\mathrm{I/P},n}^{(0)}$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
					\State Compute $R^{(0)}$, $z^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:m_sca}
						\State Update $\boldsymbol{h}_n^{(i)}$, $\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)}$, $\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
						\State Compute $R^{(i)}$, $z^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:z_waveform}
						\If{$\rho=0$}
							\State $\Delta = R^{(i)} - R^{(i-1)}$
						\Else
							\State $\Delta = z^{(i)} - z^{(i-1)}$
						\EndIf
					\Until $\lvert \Delta \rvert \le \epsilon$
					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)}$, $\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$, $\boldsymbol{w}_{\mathrm{I}}^{\star}$, $\boldsymbol{w}_{\mathrm{P}}^{\star}$
				\end{algorithmic}
			\end{algorithm}
		\end{subsection}
	\end{section}
